R code for 'Apparent physiological costs of blood parasite infection in the early-life of a vertebrate host - only in highest infections

### 2022-02-21 MS_physiology_infection.Rmd
Add files via upload

---
title: "R code for 'Apparent physiological costs of early-life blood parasite infection in a vertebrate host'"
author: "Tony Rinaud, Meinolf Ottensmann, Oliver Krüger & Nayden Chakarov"
output: html_document
---

@@

```{r packages, message=F, warning=F}
library(chron)
library(cowplot)
library(EnvStats)
library(lme4)
library(lsmeans)
library(ggalt)
library(ggdist)
library(ggeffects)
library(ggplot2)
library(ggpubr)
library(ggrepel)
library(ggridges)
library(ggsci)
library(ggsignif)
library(grid)
library(gridExtra)
library(magrittr)
library(patchwork)
library(rptR)
library(RVAideMemoire)
library(sjPlot)
library(sjlabelled)
library(sjmisc)
library(tidybayes)
library(tidyverse)
library(wesanderson)
theme_set(theme_tidybayes() + panel_border())
```

@@

## Create Table S1
## -----------------------------------------------------------------------------
tab_model(
  lm_d1,lm_d2,lm_d3,lm_d4,
  show.reflvl = T,
  show.ci50 = T ,
  show.stat = T,
  string.stat = "t",
  pred.labels = c("Intercept","Treatment [Malarone]"),
  dv.labels = c("Breathing rate","Body temperature", "\U0394 Body condition","Growth rate"),
  file = "./Physiological_parameters_in_decreasing_control_treated.html")
```

@@

```{r mixed model breathing rate, warning=F, message=F}
## Run model
## ----------------------------------------------------------------------------- 
lmer_br <- lmer(
  Breathing_rate ~ Diff_Inf_Class + Diff_Inf_Class:Treatment + 
    days_resample + Age_in_days + Weight_g + Sex + Ambient_Temperature_AvgC + Year + (1|Nest),
  data = df)

@@

```{r mixed model body temp after, warning=FALSE, message=F}
## Model 
## -----------------------------------------------------------------------------
lmer_bt = lmer(
  body_temperature ~ Diff_Inf_Class + Diff_Inf_Class:Treatment + Ambient_Temperature_AvgC + 
    days_resample + Age_in_days + Weight_g + Sex + Year + (1|Nest),
  data = df)

@@

```{r mixed model body condition, warning=FALSE, message=F}
## Model 
## -----------------------------------------------------------------------------
lmer_bc <- lmer(
  delta_body_condition ~ Diff_Inf_Class+Diff_Inf_Class:Treatment+days_resample + 
    Age_in_days+Sex+Year+(1|Nest),
  data = df)

@@

```{r mixed model body temp, warning=FALSE, message=F}
# Model 
lmer_gr = lmer(Growth_rate ~ Diff_Inf_Class + Diff_Inf_Class:Treatment + Sex + days_resample + Age_in_days + Year + (1|Nest), data= df)

@@

# Table 3
## -----------------------------------------------------------------------------
sjPlot::tab_model(
  lmer_br,lmer_bt,lmer_bc,lmer_gr,
  show.ci50 = T ,
  show.stat = T,
  string.stat = "t",
  df.method = "kr",
  dv.labels = c("Breathing rate","Body temperature","\U0394 Body condition","Growth rate"),
  file = "Table_results_lmer_physiological_parameters_p.val_kr.html")
```

@@

```{r mixed model breathing rate 2, warning=F, message=F}
## Model 
## -----------------------------------------------------------------------------
lmer_br_para = lmer(
  Breathing_rate ~ Infection_intensity.2 + Infection_intensity.2:Treatment + days_resample + 
    Age_in_days + Weight_g + Sex + Ambient_Temperature_AvgC + Year + (1|Nest), data= df)

@@

gg1_pred_para = ggplot(mod_br_para) + 
  aes(as.factor(mod_br_para$x),mod_br_para$predicted) + 
  geom_hline(yintercept = mean(mod_br_para$predicted, na.rm = T), linetype = "dashed") + 
  labs(x = "", y = "Breathing rate") + 
  geom_errorbar(aes(ymin = mod_br_para$lower_CI,ymax = mod_br_para$higher_CI),colour = "black",size = 2, width = .1) + 
  geom_errorbar(aes(ymin = mod_br_para$predicted - mod_br_para$se, ymax = mod_br_para$predicted + mod_br_para$se),
                size = 8, colour = wes_palette("Zissou1",5), width = 0,) + 
  geom_point(color = "black", outlier.shape = NA, size = 4, width = .3) + 
  theme_classic() + 
  theme(legend.position = "none",
        axis.title = element_text(size = 14),
        axis.text = element_text(size = 12),
        axis.line.x = element_blank(),
        axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"),
        plot.title = element_text(hjust = 0.5, face = "bold")) + 
  geom_segment(size = .8, aes(x = 1, y = max(mod_br_para$higher_CI, na.rm = T) + 1.2,
                              xend=5, yend = max(mod_br_para$higher_CI, na.rm = T) + 1.2)) + 
    geom_text(aes(x = 3, y = max(mod_br_para$higher_CI, na.rm = T) + 2),
              label = "n.s.", size = 5)
```

@@

gg2_pred_para = ggplot(mod_bt_para) + 
  aes(as.factor(mod_bt_para$x),mod_bt_para$predicted) + 
  geom_hline(yintercept = mean(mod_bt_para$predicted, na.rm = T), linetype = "dashed") + 
  geom_errorbar(aes(ymin = mod_bt_para$lower_CI,ymax = mod_bt_para$higher_CI),colour = "black",size = 2, width = .1) + 
  geom_errorbar(aes(ymin = mod_bt_para$predicted - mod_bt_para$se,ymax = mod_bt_para$predicted + mod_bt_para$se),
                size =8,colour = wes_palette("Zissou1",5), width = 0,) + 
  labs(x = "", y = "Body temperature") + 
  geom_point(color = "black", outlier.shape = NA, size =4, width = .3) + 
  theme_classic() + 
  theme(legend.position = "none",
        axis.title = element_text(size = 14),
        axis.text = element_text(size = 12),
        axis.line.x = element_blank(), 
        axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"),
        plot.title = element_text(hjust = 0.5, face = "bold")) + 
  geom_segment(size = .8, aes(x = 1, y = max(mod_bt_para$higher_CI, na.rm = T) + 0.2,
                              xend = 5, yend = max(mod_bt_para$higher_CI, na.rm = T) + 0.2)) + 
    geom_text(aes(x = 3, y = max(mod_bt_para$higher_CI, na.rm = T) + 0.25),
              label = "**", size = 8) + 
  geom_segment(size = .8,
                 aes(x = 1, y = max(mod_bt_para$higher_CI, na.rm = T) + 0.2, xend=1, yend = max(mod_bt_para$higher_CI, na.rm = T) + 0.05)) + 
  geom_segment(size = .8,
                 aes(x =5, y = max(mod_bt_para$higher_CI, na.rm = T) + 0.05, xend=5, yend = max(mod_bt_para$higher_CI, na.rm = T) + 0.2))
```

@@

```{r mixed model body condition change 2, warning=FALSE, message=F, echo=T}
# Model 
lmer_bc_para <- lmer(
  delta_body_condition ~ Infection_intensity.2 + Infection_intensity.2:Treatment + days_resample +
    Age_in_days + Sex + Year + (1|Nest), data= df)

@@

gg3_pred_para = ggplot(mod_bc_para) + 
  aes(as.factor(mod_bc_para$x),mod_bc_para$predicted) + 
  geom_hline(yintercept = mean(mod_bc_para$predicted, na.rm = T), linetype = "dashed") + 
  labs(x = "", y = "Δ Body condition") + 
  geom_errorbar(aes(ymin = mod_bc_para$lower_CI,ymax = mod_bc_para$higher_CI),colour = "black",size = 2, width =.1) + 
  geom_errorbar(aes(ymin = mod_bc_para$predicted-mod_bc_para$se,ymax = mod_bc_para$predicted+mod_bc_para$se),size =8,colour = wes_palette("Zissou1",5), width = 0,) + 
  geom_point(color = "black", outlier.shape = NA, size =4, width = .3) + 
  theme_classic() + 
  theme(legend.position = "none",
        axis.title = element_text(size = 14),  
        axis.text = element_text(size = 12), 
        axis.line.x = element_blank(),
        axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"),
        plot.title = element_text(hjust = 0.5, face = "bold")) + 
  geom_segment(size = .8,
                 aes(x = 1, y =-105, xend=5, yend =-105)) + 
    geom_text(aes(x =3, y =-110),
              label= "p=0.08", size = 5) + 
  geom_segment(size = .8,
                 aes(x = 1, y =-105, xend=1, yend =-105+5)) + 
  geom_segment(size = .8,
                 aes(x =5, y =-105, xend=5, yend =-105+5))
```

@@

```{r mixed model growth rate 2, warning=FALSE, message=F, echo=T}
# Model 
lmer_gr_para = lmer(
  Growth_rate ~ Infection_intensity.2 + Infection_intensity.2:Treatment +
    days_resample + Sex + Age_in_days + Year + (1|Nest), data= df)

@@

sjPlot::tab_model(lmer_br_para,lmer_bt_para,lmer_bc_para,lmer_gr_para,
                  show.ci50 = T ,
                  show.stat = T,
                  string.stat = "t",
                  p.val = "kr",
                  dv.labels = c("Breathing rate","Body temperature","\U0394 Body condition","Growth rate"),
                  file = "table_results_parasitemia_lmer_physiological_parameters_p.val_kr.html")

@@

```{r, warning=F,message=F}
tol_resdata = df
tol_resdata$Infection_intensity.2 = as.numeric(tol_resdata$Infection_intensity.2)
tol_resdata$Diff_Inf_Class = factor(tol_resdata$Diff_Inf_Class, levels = c("Increase","Peak","Decrease"))

# Second sampling parasitemia

## linear model testing effect of infection intensity at second sampling on body condition change

tolres_mod=lm(delta_body_condition~Infection_intensity.2, data=tol_resdata)

@@

## Testing the interaction between infection stages and infection intensities

## with delta body condition

tolres_deltamod=lm(delta_body_condition~Infection_intensity.2*Diff_Inf_Class, data=tol_resdata)

## comparison of slopes among infection stages

lms_delta=lstrends(tolres_deltamod,~Diff_Inf_Class:Infection_intensity.2, var= "Infection_intensity.2")

@@

tolre_deltasum=summary(lms_delta)

## comparison of slopes to zero

@@

# Plotting body condition change - second infection intensity

tolres <- ggplot(data = df[!df$Infection_intensity.2 %in% c(NA,0) & !df$Diff_Inf_Class %in% NA,],
                aes(y = delta_body_condition, x = as.numeric(Infection_intensity.2), col = Diff_Inf_Class)) + 
    geom_jitter(size = 3, alpha=0.5) + 
    geom_smooth(alpha = 0.2, size =1.5, method='lm',se = T) + 
    labs(y = "Body condition change",x = "Parasitemia \n at second sampling", col='Infection stages') + 
    scale_x_continuous(breaks=seq(2,5,1),labels= c("1","2","3","4")) + 
    scale_color_manual(labels = c("Increasing", "Peak", "Decreasing"),values = c("#3B9AB2", "#E1AF00", "#F21A00")) + 
    theme_classic() + 
    theme(legend.text = element_text(size =19),legend.title = element_text(size =22), axis.text = element_text(size =16), axis.title = element_text(size =18))

# Figure 3

@@

ggsave(fig3,filename = "./Figs/delta_body_condition_to_parasitemia_second.png",units = "px", width = 3700, height = 2800)
```

@@

```{r}
# Plotting observed values across infection stages
gg1 = ggplot(df[!df$Diff_Inf_Class %in% NA,]) + 
  aes(Diff_Inf_Class,Breathing_rate) + 
  geom_hline(yintercept = mean(df$Breathing_rate, na.rm = T), linetype = "dashed") + 
  labs(x = "", y = "Breathing rate") + 
  geom_jitter(color = "lightgrey", size = 2, width = .3) + 
  stat_summary(fun = mean, colour = "cornflowerblue", geom = "errorbar", 
               size =2.8 , width = 0.05, show.legend = FALSE, 
               fun.max = function(x) mean(x) + sd(x),
               fun.min = function(x) mean(x) - sd(x)) + 
  stat_summary(fun = mean, colour = "black", geom = "point", 
               size =5 ,show.legend = FALSE) + 
  stat_n_text() + 
  theme_classic() + 
  theme(legend.position = "none", axis.title = element_text(size = 14),  axis.text = element_text(size = 12), axis.line.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"), plot.title = element_text(hjust = 0.5, face = "bold"))

@@

# Figure S1

@@

# Plotting observed values across infection intensities

@@

# Figure S2

@@

# Plotting effect sizes of 'infection stages' models

@@

# Figure S3

figs3=pm1+pm2+pm3+pm4 + plot_annotation(tag_levels = 'A')& 
  theme(plot.tag = element_text(size = 16, face = "bold"))

@@

# Plotting effect sizes of 'infection intensities' models

@@

# Figure S4

@@

```{r}

rTemp=read.csv2("C://Users/Tony/Documents/Phd Bielefeld/Data manip/Fieldwork_2019/Repeatability_temperatures.csv", h=T, dec='.')

@@

## Estimating repeatability of paired measures
## -----------------------------------------------------------------------------
rpt(Temperature ~ (1|ID), grname = "ID", data = rTemp, npermut = 1000, datatype = 'Gaussian')

@@

>>>>

---
title: "R code for 'Apparent physiological costs of blood parasite infection in the early-life of a vertebrate host - only in highest infections'"
author: "Tony Rinaud, Meinolf Ottensmann, Oliver Krüger & Nayden Chakarov"
output: html_document
---

@@

```{r packages, message=F, warning=F}
library(chron)
library(cowplot)
library(EnvStats)
library(lme4)
library(lsmeans)
library(ggalt)
library(ggdist)
library(ggeffects)
library(ggplot2)
library(ggpubr)
library(ggrepel)
library(ggridges)
library(ggsci)
library(ggsignif)
library(grid)
library(gridExtra)
library(magrittr)
library(patchwork)
library(plyr)
library(rptR)
library(RVAideMemoire)
library(sjPlot)
library(sjlabelled)
library(sjmisc)
library(tidybayes)
library(tidyverse)
library(wesanderson)
theme_set(theme_tidybayes() + panel_border())
```

@@

## Create Table S1
## -----------------------------------------------------------------------------
tab_model(
  lm_d1,lm_d2,lm_d3,lm_d4,
  show.reflvl = T,
  show.ci50 = T ,
  show.stat = T,
  string.stat = "t",
  pred.labels = c("Intercept","Treatment [Malarone]"),
  dv.labels = c("Breathing rate","Body temperature", "\U0394 Body condition","Growth rate"),
  file = "./Tables/Physiological_parameters_in_decreasing_control_treated.html")
```

@@

```{r mixed model breathing rate}
## Run model
## ----------------------------------------------------------------------------- 
lmer_br <- lmer(
  Breathing_rate ~ Diff_Inf_Class + Diff_Inf_Class:Treatment + 
    days_resample + Age_in_days + Weight_g + Sex + Ambient_Temperature_AvgC + Year + (1|Nest),
  data = df)

@@

```{r mixed model body temp}
## Model 
## -----------------------------------------------------------------------------
lmer_bt = lmer(
  body_temperature ~ Diff_Inf_Class + Diff_Inf_Class:Treatment + Ambient_Temperature_AvgC + 
    days_resample + Age_in_days + Weight_g + Sex + Year + (1|Nest),
  data = df)

@@

```{r mixed model body condition}
## Model 
## -----------------------------------------------------------------------------
lmer_bc <- lmer(
  delta_body_condition ~ Diff_Inf_Class+Diff_Inf_Class:Treatment+days_resample + 
    Age_in_days+Sex+Year+(1|Nest),
  data = df)

@@

```{r mixed model growth rate}
# Model 
lmer_gr = lmer(Growth_rate ~ Diff_Inf_Class + Diff_Inf_Class:Treatment + Sex + days_resample + Age_in_days + Year + (1|Nest), data= df)

@@

# Table 3
## -----------------------------------------------------------------------------
sjPlot::tab_model(
  lmer_br,lmer_bt,lmer_bc,lmer_gr,
  show.ci50 = T ,
  show.stat = T,
  string.stat = "t",
  df.method = "kr",
  dv.labels = c("Breathing rate","Body temperature","\U0394 Body condition","Growth rate"),
  file = "./Tables/Table_results_lmer_physiological_parameters_p.val_kr.html")
```

@@

```{r mixed model breathing rate 2}
## Model 
## -----------------------------------------------------------------------------
lmer_br_para = lmer(
  Breathing_rate ~ Infection_intensity.2 + Infection_intensity.2:Treatment + days_resample + 
    Age_in_days + Weight_g + Sex + Ambient_Temperature_AvgC + Year + (1|Nest), data= df)

@@

gg1_pred_para = ggplot(mod_br_para) + 
  aes(as.factor(mod_br_para$x),mod_br_para$predicted) + 
  geom_hline(yintercept = mean(mod_br_para$predicted, na.rm = T), linetype = "dashed") + 
  labs(x = "", y = "Breathing rate") + 
  geom_errorbar(aes(ymin = mod_br_para$lower_CI,ymax = mod_br_para$higher_CI),colour = "black",size = 2, width = .1) + 
  geom_errorbar(aes(ymin = mod_br_para$predicted - mod_br_para$se, ymax = mod_br_para$predicted + mod_br_para$se),
                size = 8, colour = wes_palette("Zissou1",5), width = 0,) + 
  geom_point(color = "black", size = 4) + 
  theme_classic() + 
  theme(legend.position = "none",
        axis.title = element_text(size = 14),
        axis.text = element_text(size = 12),
        axis.line.x = element_blank(),
        axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"),
        plot.title = element_text(hjust = 0.5, face = "bold")) + 
  geom_segment(size = .8, aes(x = 1, y = max(mod_br_para$higher_CI, na.rm = T) + 1.2,
                              xend=5, yend = max(mod_br_para$higher_CI, na.rm = T) + 1.2)) + 
    geom_text(aes(x = 3, y = max(mod_br_para$higher_CI, na.rm = T) + 2),
              label = "n.s.", size = 5)
```

@@

gg2_pred_para = ggplot(mod_bt_para) + 
  aes(as.factor(mod_bt_para$x),mod_bt_para$predicted) + 
  geom_hline(yintercept = mean(mod_bt_para$predicted, na.rm = T), linetype = "dashed") + 
  geom_errorbar(aes(ymin = mod_bt_para$lower_CI,ymax = mod_bt_para$higher_CI),colour = "black",size = 2, width = .1) + 
  geom_errorbar(aes(ymin = mod_bt_para$predicted - mod_bt_para$se,ymax = mod_bt_para$predicted + mod_bt_para$se),
                size =8,colour = wes_palette("Zissou1",5), width = 0,) + 
  labs(x = "", y = "Body temperature") + 
  geom_point(color = "black", size =4) + 
  theme_classic() + 
  theme(legend.position = "none",
        axis.title = element_text(size = 14),
        axis.text = element_text(size = 12),
        axis.line.x = element_blank(), 
        axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"),
        plot.title = element_text(hjust = 0.5, face = "bold")) + 
  geom_segment(size = .8, aes(x = 1, y = max(mod_bt_para$higher_CI, na.rm = T) + 0.2,
                              xend = 5, yend = max(mod_bt_para$higher_CI, na.rm = T) + 0.2)) + 
    geom_text(aes(x = 3, y = max(mod_bt_para$higher_CI, na.rm = T) + 0.25),
              label = "**", size = 8) + 
  geom_segment(size = .8,
                 aes(x = 1, y = max(mod_bt_para$higher_CI, na.rm = T) + 0.2, xend=1, yend = max(mod_bt_para$higher_CI, na.rm = T) + 0.05)) + 
  geom_segment(size = .8,
                 aes(x =5, y = max(mod_bt_para$higher_CI, na.rm = T) + 0.05, xend=5, yend = max(mod_bt_para$higher_CI, na.rm = T) + 0.2))
```

@@

```{r mixed model body condition change 2}
# Model 
lmer_bc_para <- lmer(
  delta_body_condition ~ Infection_intensity.2 + Infection_intensity.2:Treatment + days_resample +
    Age_in_days + Sex + Year + (1|Nest), data= df)

@@

gg3_pred_para = ggplot(mod_bc_para) + 
  aes(as.factor(mod_bc_para$x),mod_bc_para$predicted) + 
  geom_hline(yintercept = mean(mod_bc_para$predicted, na.rm = T), linetype = "dashed") + 
  labs(x = "", y = "Δ Body condition") + 
  geom_errorbar(aes(ymin = mod_bc_para$lower_CI,ymax = mod_bc_para$higher_CI),colour = "black",size = 2, width =.1) + 
  geom_errorbar(aes(ymin = mod_bc_para$predicted-mod_bc_para$se,ymax = mod_bc_para$predicted+mod_bc_para$se),size =8,colour = wes_palette("Zissou1",5), width = 0,) + 
  geom_point(color = "black", size =4) + 
  theme_classic() + 
  theme(legend.position = "none",
        axis.title = element_text(size = 14),  
        axis.text = element_text(size = 12), 
        axis.line.x = element_blank(),
        axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"),
        plot.title = element_text(hjust = 0.5, face = "bold")) + 
  geom_segment(size = .8,
                 aes(x = 1, y =-105, xend=5, yend =-105)) + 
    geom_text(aes(x =3, y =-110),
              label= "p=0.08", size = 5) + 
  geom_segment(size = .8,
                 aes(x = 1, y =-105, xend=1, yend =-105+5)) + 
  geom_segment(size = .8,
                 aes(x =5, y =-105, xend=5, yend =-105+5))
```

@@

```{r mixed model growth rate 2}
# Model 
lmer_gr_para = lmer(
  Growth_rate ~ Infection_intensity.2 + Infection_intensity.2:Treatment +
    days_resample + Sex + Age_in_days + Year + (1|Nest), data= df)

@@

sjPlot::tab_model(lmer_br_para,lmer_bt_para,lmer_bc_para,lmer_gr_para,
                  show.ci50 = T ,
                  show.stat = T,
                  string.stat = "t",
                  p.val = "kr",
                  dv.labels = c("Breathing rate","Body temperature","\U0394 Body condition","Growth rate"),
                  file = "./Tables/table_results_parasitemia_lmer_physiological_parameters_p.val_kr.html")

@@

```{r, warning=F,message=F}

## Infection intensity as numerical variable
## -----------------------------------------------------------------------------
tol_resdata = df
tol_resdata$Infection_intensity.2 = as.numeric(tol_resdata$Infection_intensity.2)
tol_resdata$Diff_Inf_Class = factor(tol_resdata$Diff_Inf_Class, levels = c("Increase","Peak","Decrease"))

## Modeling host health to Infection intensity
## -----------------------------------------------------------------------------
tolres_mod=lm(delta_body_condition~Infection_intensity.2, data=tol_resdata)

@@

## Modeling host health to Infection intensity : Infection stages
## -----------------------------------------------------------------------------
tolres_deltamod=lm(delta_body_condition~Infection_intensity.2*Diff_Inf_Class, data=tol_resdata)

## Comparison of intercepts
## -----------------------------------------------------------------------------
emm=emmeans(tolres_deltamod, "Diff_Inf_Class", at=list(Infection_intensity.2=0))

pairs(emm)

## Pairwise comparison of slopes
## -----------------------------------------------------------------------------
lms_delta=lstrends(tolres_deltamod,~Diff_Inf_Class:Infection_intensity.2, var= "Infection_intensity.2")

@@

## Comparison of slopes to zero
## -----------------------------------------------------------------------------
tolre_deltasum=summary(lms_delta)

@@

## Plotting body condition change with the interaction second infection intensity - infection stage
## -----------------------------------------------------------------------------

tolres <- ggplot(data = df[!df$Infection_intensity.2 %in% c(NA,0) & !df$Diff_Inf_Class %in% NA,],
                aes(y = delta_body_condition, x = as.numeric(Infection_intensity.2), col = Diff_Inf_Class)) + 
    geom_jitter(size = 3, alpha=0.5) + 
    geom_smooth(alpha = 0.2, size =1.5, method='lm',se = T, width=0.2) + 
    facet_wrap(facets = 'Diff_Inf_Class')+
    labs(y = "Body condition change",x = "Parasitemia \n at second sampling", col='Infection stages') + 
    scale_x_continuous(breaks=seq(2,5,1),labels= c("1","2","3","4")) + 
    scale_color_manual(labels = c("Increasing", "Peak", "Decreasing"),values = c("#3B9AB2", "#E1AF00", "#F21A00")) + 
    theme_pubr() +
    annotate(geom = 'segment', y = -Inf, yend = Inf, color = 'black', x = Inf, xend = Inf, size = 0.5) +
    annotate(geom = 'segment', y = -Inf, yend = Inf, color = 'black', x = -Inf, xend = -Inf, size = 0.5) +
    theme(legend.position = "none", 
          legend.text = element_text(size =19),
          legend.title = element_text(size =22), 
          axis.text = element_text(size =16), 
          axis.title = element_text(size =18),
          strip.text = element_text(face="bold", size=14))

g <- ggplot_gtable(ggplot_build(tolres))
stripr <- which(grepl('strip-t', g$layout$name))
fills <- c("#3B9AB2", "#E1AF00", "#F21A00")
k <- 1
for (i in stripr) {
 j <- which(grepl('rect', g$grobs[[i]]$grobs[[1]]$childrenOrder))
g$grobs[[i]]$grobs[[1]]$children[[j]]$gp$fill <- fills[k]
k <- k+1
}

g=arrangeGrob(g)

## Saving Figure 3
## -----------------------------------------------------------------------------

@@

ggsave(g,filename = "./Figs/delta_body_condition_to_parasitemia_second.png",units = "px", width = 3700, height = 2800)
```

@@

```{r}
## Plotting observed values across infection stages
## -----------------------------------------------------------------------------

gg1 = ggplot(df[!df$Diff_Inf_Class %in% NA,]) + 
  aes(Diff_Inf_Class,Breathing_rate) + 
  geom_hline(yintercept = mean(df$Breathing_rate, na.rm = T), linetype = "dashed") + 
  labs(x = "", y = "Breathing rate") + 
  geom_jitter(color = "lightgrey", size = 2, width = .3) + 
  stat_summary(fun = mean, colour = "cornflowerblue", geom = "errorbar", 
               size =2.8 , width = 0.05, show.legend = FALSE, 
               fun.max = function(x) mean(x) + sd(x),
               fun.min = function(x) mean(x) - sd(x)) + 
  stat_summary(fun = mean, colour = "black", geom = "point", 
               size =5 ,show.legend = FALSE) + 
  stat_n_text() + 
  theme_classic() + 
  theme(legend.position = "none", axis.title = element_text(size = 14),  axis.text = element_text(size = 12), axis.line.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"), plot.title = element_text(hjust = 0.5, face = "bold"))

@@

## Saving Figure S1
## -----------------------------------------------------------------------------

@@

## Plotting observed values across infection intensities
## -----------------------------------------------------------------------------

@@

## Saving figure S2
## -----------------------------------------------------------------------------

@@

## Plotting effect sizes of 'infection stages' models
## -----------------------------------------------------------------------------

@@

## Saving Figure S3
## ----------------------------------------------------------------------------- 
figs3=pm1+pm2+pm3+pm4 + plot_annotation(tag_levels = 'A')& 
  theme(plot.tag = element_text(size = 16, face = "bold"))

@@

## Plotting effect sizes of 'infection intensities' models
## -----------------------------------------------------------------------------

@@

## Figure S4
## -----------------------------------------------------------------------------

@@

```{r, message=F, warnings=F}
## Loading repeated temperature measures 
## -----------------------------------------------------------------------------

rTemp=read.csv2("./Repeatability_temperatures.csv", h=T, dec='.')

@@

## Estimating repeatability of paired measures
## -----------------------------------------------------------------------------

rpt(Temperature ~ (1|ID), grname = "ID", data = rTemp, npermut = 1000, datatype = 'Gaussian')

@@

## Values of mean and standard deviation of average paired body temperatures
## -----------------------------------------------------------------------------
